---
title: "Donwloading genomes from an RSAT server"
author: "Bruno Contreras Moreira"
date: '`r Sys.Date()`'
output:
  html_document:
    self_contained: false
    fig_caption: true
    highlight: kate
    theme: cerulean
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
  pdf_document:
    fig_caption: yes
    highlight: zenburn
    toc: yes
    toc_depth: 5
---

This procedure allows the installation of any genome available in a RSAT Web server.
This is usually the fastest way of getting a genome installed, as this way oligo and dyad frequencies are not computed, they are copied over instead.

To find out which genomes are available visit your favorite RSAT server and in the left menu 
click on 'Genomes and genes: supported organisms' to get an up-to-date table. The organism
name you need for the command below is the one in column ID:

```{r, engine='bash', eval=FALSE}
download-organism \\
   -server http://rsat.eead.csic.es/plants \\
   -org Arabidopsis_thaliana.TAIR10.29
```


The newly installed species will be added to $RSAT/data/supported_organisms.tab and should be listed with the following 
command-line:

```{r, engine='bash', eval=FALSE}
supported-organisms
```

*********
