---
title: "Donwloading genomes from an RSAT server or genome repository"
author: "Bruno Contreras Moreira"
date: '`r Sys.Date()`'
output:
  html_document:
    self_contained: false
    fig_caption: true
    highlight: kate
    theme: cerulean
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
  pdf_document:
    fig_caption: yes
    highlight: zenburn
    toc: yes
    toc_depth: 5
---

This procedure allows the installation of any genome available in a RSAT Web server or genome repository.
This is usually the fastest way of getting a genome installed, as this way oligo and dyad frequencies are not computed, they are copied over instead.

To check which servers and repos are available you can:
```{r, engine='bash', eval=FALSE}
supported-organisms-server -servers
```

To find out which genomes are currently available please try:
```{r, engine='bash', eval=FALSE}
download-organism -listall
```

You will get a tabular output where the 1st column is the URL of the RSAT server or genome repository, 
the 2nd column is the genomeID, the 3rd column is the source of the genome, and the 4th column is the taxonomic classification of the organism:

    https://rsat.eead.csic.es/plantsdata/	Actinidia_chinensis.Red5_PS1_1.69.0.60	ensemblgenomes	Eukaryota;Viridiplantae;Streptophyta;Embryophyta;Tracheophyta;Spermatophyta;Magnoliopsida;eudicotyledons;Gunneridae;Pentapetalae;asterids;Ericales;Actinidiaceae;Actinidia;Actinidia chinensis
    https://rsat.eead.csic.es/plantsdata/	Aegilops_tauschii.Aetv4.0.60	ensemblgenomes	Eukaryota;Viridiplantae;Streptophyta;Embryophyta;Tracheophyta;Spermatophyta;Magnoliophyta;Liliopsida;Poales;Poaceae;BOP clade;Pooideae;Triticodae;Triticeae;Triticinae;Aegilops;Aegilops tauschii
    https://rsat.eead.csic.es/plantsdata/	Amborella_trichopoda.AMTR1.0.60	ensemblgenomes	Eukaryota;Viridiplantae;Streptophyta;Embryophyta;Tracheophyta;Spermatophyta;Magnoliopsida;Amborellales;Amborellaceae;Amborella;Amborella trichopoda

<!--available visit your favorite RSAT server and in the left menu 
click on 'Genomes and genes: supported organisms' to get an up-to-date table.-->

You can now install a selected organsm as follows:
```{r, engine='bash', eval=FALSE}
download-organism -org Actinidia_chinensis.Red5_PS1_1.69.0.60
```

The newly installed species will be added to $RSAT/data/supported_organisms.tab and should be listed with the following 
command-line:

```{r, engine='bash', eval=FALSE}
supported-organisms
```


